Forecasting Multi-District Elections

### 2019-11-25 outputs/paper/paper.Rmd
Add Pats changes

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Forecasting Multi-District Elections"
thanks: "We thank the Social Research Centre, and in particular Ben Phillips, for graciously providing data. Thank you to Monica Alexander, John McAndrews, Benjamin Stevens, Michael Donnelly, as well as seminar participants at the University of Toronto Political Behaviour Group and the 2019 POP AusPSA Standing Group Annual Workshop for their assistance and helpful suggestions. Our code and datasets are available at: https://github.com/RohanAlexander/ForecastingMultiDistrictElections. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
author:
- name: Rohan Alexander
  affiliation: University of Toronto
- name: Patrick Dumont
  affiliation: Australian National University
- name: Lauren Kennedy
  affiliation: Columbia University
- name: Patrick Leslie
  affiliation: Australian National University
abstract: "The overall outcome of an election in a multi-district system turns on the number of electoral divisions won by each party. Despite this, traditional political opinion polls tend to focus on broad national-level estimates of support for major parties. In this paper we develop a framework to characterise a useful forecasting model of multi-district elections. We then implement an approach to forecast the number of electoral divisions won by each of the larger political parties in Australia at the 2019 Federal Election. Our approach first uses survey data and multi-level regression with post-stratification (MRP) to estimate electoral-division-level first-preference shares. To account for Australia's use of preferential voting, we then use a model that we trained to estimate electoral-division-level two-party-preferred shares. We find that our approach performs well out-of-sample, and it has additional advantages over traditional polling including improved interpretability, transparency, and better communication of statistical uncertainty. Our framework allows the consistent evaluation of forecasting models of elections in a multi-district system. Finally, our paper also improves our understanding of the circumstances in which MRP is appropriate, as we find that despite the bias of voter advice applications, and despite the relatively small number of respondents per electoral division for usually political opinion polls, both can still provide informative results on an electoral division basis."
keywords: "Multi-district elections, political opinion polls, forecasting, multi-level regression with post-stratification, Australia."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: references.bib
biblio-style: "apalike"
endnote: no

@@

<!-- Possibly no need to include this for job app

@@

Finally, in terms of communication, we have provided some variations designed to ensure that the probability nature of our model cannot be separated from central estimates. However, this is just a first step and there is much more that could be done, including survey work and field testing to examine how this could be done in a better way. -->

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Forecasting Multi-District Elections"
thanks: "We thank the Social Research Centre, and in particular Ben Phillips, for graciously providing data. Thank you to Monica Alexander, Lauren Kennedy, John McAndrews, Benjamin Stevens, Michael Donnelly, as well as seminar participants at the University of Toronto Political Behaviour Group and the 2019 POP AusPSA Standing Group Annual Workshop for their assistance and helpful suggestions. Our code and datasets are available at: https://github.com/RohanAlexander/ForecastingMultiDistrictElections. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
author:
- name: Rohan Alexander
  affiliation: University of Toronto
- name: Patrick Dumont
  affiliation: Australian National University
- name: Patrick Leslie
  affiliation: Australian National University
abstract: "The overall outcome of an election in a multi-district system turns on the number of electoral divisions won by each party. Despite this, traditional political opinion polls tend to focus on broad national-level estimates of support for major parties. In this paper we develop a framework to characterise a useful forecasting model of multi-district elections. We then implement an approach to forecast the number of electoral divisions won by each of the larger political parties in Australia at the 2019 Federal Election. Our approach first uses survey data and multi-level regression with post-stratification (MRP) to estimate electoral-division-level first-preference shares. To account for Australia's use of preferential voting, we then use a model that we trained to estimate electoral-division-level two-party-preferred shares. We find that our approach performs well out-of-sample, and it has additional advantages over traditional polling including improved interpretability, transparency, and better communication of statistical uncertainty. Our framework allows the consistent evaluation of forecasting models of elections in a multi-district system. Finally, our paper also improves our understanding of the circumstances in which MRP is appropriate, as we find that despite the bias of voter advice applications, and despite the relatively small number of respondents per electoral division for usually political opinion polls, both can still provide informative results on an electoral division basis."
keywords: "Multi-district elections, political opinion polls, forecasting, multi-level regression with post-stratification, Australia."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: references.bib
biblio-style: "apalike"
endnote: no

@@

@@

Finally, in terms of communication, we have provided some variations designed to ensure that the probability nature of our model cannot be separated from central estimates. However, this is just a first step and there is much more that could be done, including survey work and field testing to examine how this could be done in a better way.
